Neural networks for solving regression and classification problems

### 2022-11-18 doc/paper.tex
Ad

%100 epochs are more or less the same. As the largest change in MSE occurs in the first 50 epochs as seen in Fig.~\ref{figall}, perhaps the other schedulers are given enough time to catch up as the best performing schedulers, such as Adagrad, starts slowing down the rate at which the MSE is decreased. However, as can be seen in Fig.~\ref{heatmap}, Adagrad offers a 12\% \footnote{$\frac{constant MSE}{adagrad MSE} * 100 = \frac{0.018}{0.015} * 100 = 12\%$} decrease in MSE compared to the constant scheduler. It is clear from the results thus far that Adagrad is the best scheduler for approximating the Franke function when using linear regression with gradient descent. We believe that the reason Adagrad wins out is that these result are based on training for 100 epochs. The downfall of Adagrad in the literature seems to be that the aggressive decaying of the learning rate hinders a quick convergence deeper into training \cite{datasci}. We are thus cautionary to claim that Adagrad will do the best job over a much larger amount of epochs when compared to adaptive schedulers that claim to improve this aspect such as Adam.

% To test this, we compared Adagrad with Adam over 5000 epochs, cross validated for 5 folds, as can be seen in Fig.~\ref{adam_v_adagrad}. Both schedulers perform almost equally, with Adagrad reaching a slightly lower MSE of 0.011 for the test data when compared to Adam's 0.012. It could be argued that 5000 epochs is not enough for the improvements of Adam to be noticeable, as the MSE could still be pushed much lower. However, for these computationally expensive runs it is clear that Adagrad is the scheduler of choice, especially considering our previous conclusion that Adagrad used less time to train. It should be noted that scikit learn's implementation outperforms both our implementation of Adagrad and Adam, with an MSE of 0.004. This could be due to a more favorable wight initialization in scikits model, along with additional optimizations implemented in their library. That we don't beat the analytical solution is no surprise, as we have limited ourself to a polynomial approximation of the Franke Function with 56 features. Our MSE might approach the analytical MSE, but this might take an unreasonable amount of epochs considering the computational runtime. Still, we have obtained an MSE lower than the Newton method's result of 0.020, even though it was at a much greater computation. Next, we investigate the use of linear regression in a neural network with hidden nodes, such that we can free ourselves of the limitations of the polynomial approximation.

@@

\begin{table*}[h]
\caption{This table shows the file which created every plot in the report}
\begin{center}
\label{allparamstable}
\begin{tabular}{c | l l l}
Figure & Shell command \\
\hline
\ref{verification} & \texttt{python3 verification.py}\\
\ref{constant_v_momentum} & \texttt{python3 constant\_v\_momentum.py}\\
\ref{batch_constant_v_momentum} & \texttt{python3 constant\_v\_momentum.py}\\
\ref{heatmap} & \texttt{python3 task\_a.py}\\
\ref{adam_v_adagrad} & \texttt{python3 unknown.py}\\
\ref{msebymodelfranke} & \texttt{python3 bycomplexityfranke.py}\\
\ref{predterrain} & \texttt{python3 task\_b.py}\\
\ref{cancerarchcompsigmoid} & \texttt{python3 bycomplexitycancer.py}\\
\ref{cancerarchcomp} & \texttt{python3 bycomplexitycancer.py}\\
\ref{cancerconf} & \texttt{python3 task\_d.py}\\
\ref{cancerlogneur} & \texttt{python3 task\_d.py}\\
\ref{cancerconflog} & \texttt{python3 task\_d.py}\\
\ref{sgdbatch} & \texttt{python3 task\_a.py}\\
\hline
\end{tabular}
\end{center}
\end{table*}

\begin{figure}[H]
\centerline{\includegraphics[width=5in]{figure/SGD_batch_size_100e.png}}
\caption{MSE over epochs for different batch sizes, for all different schedulers}
\label{sgdbatch}
\end{figure}

\begin{figure}[H]
\centerline{\includegraphics[width=5in]{figure/5000e_adam_v_adagrad.png}}
\caption{MSE test error over 5000 epochs for Adam and Adagrad schedulers}
\label{adam_v_adagrad}
\end{figure}

>>>>

@@

\begin{table*}[h]
\caption{This table shows the file which created every plot in the report}
\begin{center}
\label{allparamstable}
\begin{tabular}{c | l l l}
Figure & Shell command \\
\hline
\ref{verification} & \texttt{python3 verification.py}\\
\ref{constant_v_momentum} & \texttt{python3 constant\_v\_momentum.py}\\
\ref{batch_constant_v_momentum} & \texttt{python3 constant\_v\_momentum.py}\\
\ref{heatmap} & \texttt{python3 task\_a.py}\\
\ref{msebymodelfranke} & \texttt{python3 bycomplexityfranke.py}\\
\ref{predterrain} & \texttt{python3 task\_b.py}\\
\ref{cancerarchcompsigmoid} & \texttt{python3 bycomplexitycancer.py}\\
\ref{cancerarchcomp} & \texttt{python3 bycomplexitycancer.py}\\
\ref{cancerconf} & \texttt{python3 task\_d.py}\\
\ref{cancerlogneur} & \texttt{python3 task\_d.py}\\
\ref{cancerconflog} & \texttt{python3 task\_d.py}\\
\ref{sgdbatch} & \texttt{python3 task\_a.py}\\
\ref{adam_v_adagrad} & \texttt{python3 linreg\_franke.py}\\
\hline
\end{tabular}
\end{center}
\end{table*}

\begin{figure}[H]
\centerline{\includegraphics[width=7in]{figure/SGD_batch_size_100e.png}}
\caption{MSE over epochs for different batch sizes, for all different schedulers}
\label{sgdbatch}
\end{figure}

\begin{figure}[H]
\centerline{\includegraphics[width=7in]{figure/5000e_adam_v_adagrad.png}}
\caption{MSE test error over 5000 epochs for Adam and Adagrad schedulers}
\label{adam_v_adagrad}
\end{figure}
